---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# titled.tuesday

<!-- badges: start -->
<!-- badges: end -->

The `titled.tuesday` R package is a database of Titled Tuesday games and an interface with the [Chess.com API](https://www.chess.com/news/view/published-data-api). It's capable of downloading and parsing data such as:

* Titled Tuesday standings;

* Titled Tuesday games, including the players, their ratings, and the moves played;

* All games ever played by any player on chess.com;

* All titled usernames registered on chess.com.

If you just want the data: raw Titled Tuesday PGNs are stored in the [data-raw folder](https://github.com/IgorRigolon/titled.tuesday/tree/main/data-raw), and other clean data is stored in the [output folder](https://github.com/IgorRigolon/titled.tuesday/tree/main/output).

## Installation

You can install the development version of `titled.tuesday` from GitHub with:

``` r
install.packages("devtools")
devtools::install_github("IgorRigolon/titled.tuesday")
```

## Usage

To download all Titled Tuesday standings, run

```{r example, eval = FALSE}
library(titled.tuesday)

dat <- tt_results()
```

To download all Titled Tuesday games since 2023, run

```{r example2, eval = FALSE}
dat <- tt_games(years = c(2023, 2024))
```

To download all games ever played by titled players on Chess.com, simply use the `tt_only` option (very heavy)

```{r example3, eval = FALSE}
dat <- tt_games(tt_only = FALSE, years = "all")
```

If you need the full PGNs with all moves from each game, use the `include_pgn` option. Note that this makes the final product significantly heavier.

```{r example4, eval = FALSE}
dat <- tt_games(years = 2024, include_pgn = TRUE)
```

If you only want games from a few players, use the `usernames` option, which also speeds up the download by a lot.

```{r example5, eval = FALSE}
dat <- tt_games(usernames = c("hikaru", "jospem"))

# not limited to titled players

dat <- tt_games(usernames = "your_username", tt_only = FALSE)
```

## How it works

### Results

First, the `get_tournaments` function crawls through all pages (the number of pages will have to be updated manually, there are currently 18) of the [Chess.com TT Tournaments page](https://www.chess.com/tournament/live/titled-tuesdays) and get the tournament code for each TT, which makes up their URL.

Then, the `get_download_url` function calls the API to obtain the number of rounds in each TT, and returns a final URL, which is used as an API call by `tt_results`.

### Games

The Chess.com Tournaments API only sends results for the final round of each Titled Tuesday. To get all games, I obtain the list of all titled usernames with `get_titled_players`, and then ask the API for all their games using `get_games`. The `tt_games` function simply loops over all titled players and stacks up their games.


