---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# titled.tuesday

<!-- badges: start -->
<!-- badges: end -->

The `titled.tuesday` R package is a database of Titled Tuesday games and an interface with the [Chess.com API](https://www.chess.com/news/view/published-data-api). It's capable of downloading and parsing data such as:

* Titled Tuesday standings;

* Titled Tuesday games, including the players, their ratings, and the moves played;

* All games ever played by any player on chess.com;

* All titled usernames registered on chess.com.

If you just want the data: raw Titled Tuesday PGNs are stored in the [data-raw folder](https://github.com/IgorRigolon/titled.tuesday/tree/main/data-raw), and other clean data is stored in the [output folder](https://github.com/IgorRigolon/titled.tuesday/tree/main/output).

## Installation

You can install the development version of `titled.tuesday` from GitHub with:

``` r
install.packages("devtools")
devtools::install_github("IgorRigolon/titled.tuesday")
```

## Usage

To download all Titled Tuesday standings, run

```{r example, eval = FALSE}
library(titled.tuesday)

dat <- tt_results()
```

To download all Titled Tuesday games since 2023, run

```{r example2, eval = FALSE}
dat <- tt_games(years = c(2023, 2024))
```

To download all games played by Hikaru on Chess.com since 2023, run

```{r example3, eval = FALSE}
dat <- player_games(years = 2023:2024, usernames = "hikaru")
```

Or you can request multiple players at once

```{r example4, eval = FALSE}
dat <- player_games(usernames = c("vladimirkramnik", "jospem"))
```

To download a list of all titled players on chess.com, run

```{r example5, eval = FALSE}
dat <- titled_players()
```

## How it works

### Results

First, the `get_tournaments` function crawls through all pages (the number of pages will have to be updated manually, there are currently 18) of the [Chess.com TT Tournaments page](https://www.chess.com/tournament/live/titled-tuesdays) and get the tournament code for each TT, which makes up their URL.

Then, the `get_download_url` function calls the API to obtain the number of rounds in each TT, and returns a final URL, which is used as an API call by `tt_results`.

### Games of a particular player

The Chess.com Tournaments API only sends results for the final round of each Titled Tuesday. The `get_games` function asks the API for all games of an individual player. The `player_games` function simply loops over usernames and stacks up their games.

### Titled Tuesday

I manually downloaded all PGNs from the chess.com website and saved them to the data-raw folder. The `tt_games` function only downloads and parses them.
